Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} model system

### 2014-04-25 trunk/paper_enahpc14/Sec4:Experimental-results.tex
Manuel's changes

We  approach  the  assessment  of  the energy  footprint  and  overall
performance   of  \textsc{Cosmo-art}   with  two   important  metrics:
\textit{time-to-solution} (TTS) and \textit{energy-to-solution} (ETS).
TTS refers to  the total wall clock time  of the application execution
time. ETS  is the amount of  energy spent to  achieve results.  Energy
consumption  is  assessed by  sampling  the  instantaneous peak  power
during execution which  is then averaged and multiplied  by the TTS to
determine  ETS.   Whenever  possible,  multiple production  runs  were
performed  to  illustrate the  reproducibility  of  the baseline,  and
quantify the  significant uncertainties  in the power  measurement, as
dictated by the available technology.

\subsection{Time-energy analysis of \textsc{Cosmo-art}}
\label{subsec:4.2}

>>>>

We  approach  the  assessment  of  the energy  footprint  and  overall
performance   of   \cosmoart   with  two   important  metrics:
\textit{time-to-solution} (TTS) and \textit{energy-to-solution} (ETS).
TTS refers to  the total wall clock time  of the application execution
time. ETS  is the amount of  energy spent to  achieve results.  Energy
consumption  is  assessed by  sampling  the  instantaneous peak  power
during execution which  is then averaged and multiplied  by the TTS to
determine  ETS.   Whenever  possible,  multiple production  runs  were
performed  to  illustrate the  reproducibility  of  the baseline,  and
quantify the  significant uncertainties  in the power  measurement, as
dictated by the available technology.

\subsection{Time-power-energy analysis of \textsc{Cosmo-art}}
\label{subsec:4.2}
